Introducing SCM to a small company

### 2012-01-11 article.tex
More background

The software is the messaging portion of the phone related to recieving and sending textmessages in various forms over \emph{IM-networks} and  \emph{sms}. There are plans to integrate facebook as well.
The rapidly changing standards and lack of documentation from the IM-vendors make this a time consuming job and the software needs to be updated on a regular basis to support the new protocols.
In the beginning there was only one version of the application that was supported but now they have implemented some new features that old phones can't handle but these versions still needs updates to keep supporting the old features.

@@

\subsection{Background}
The identification part of the plan contains useful information about how objects should be treated. One must decide whether or not the object should be under version control. When this should be decided one should ask the question “Is it necessary to have this object under version control in order to be able to build the complete, working release?”. If the answer to that question is yes, then the object should be configuration item (an item under version control).
Usually, the major part of the object should be under version control. What usually shouldn't be under version control is items such as PM, mails, announcements, memos.

>>>>

The software is the messaging portion of the phone related to recieving and sending textmessages in various forms over \emph{IM-networks} and  \emph{sms}. There are plans to integrate facebook as well.
The rapidly changing standards and lack of documentation from the IM-vendors make this a time consuming job and the software needs to be updated on a regular basis to support the new protocols.
In the beginning there was only one version of the application that was supported but now they have implemented some new features that old phones can't handle but these versions still needs updates to keep supporting the old features.
The software is developed in modules with small groups working on separate modules such as the UI and the different backends for various protocols.
The separation is ok the modules can be developed separately most of the time but occasionally synchronisation is needed between releases for API changes or new features affecting the backends.
If synchronisation is needed for API changes and the like it's solved in an ad hoc fashion by copying files on thumbdrives or internal emails.
The documentation is modified by whoever changes the API as microsoft doc files on a central fileserver.
When a release is needed the different modules are copied to a central computer and some persons from each team try to merge together these files by hand until they can produce a build that works.

\subsection{documentation}
The documentation is modified by whoever changes the API as microsoft doc files on a central fileserver.
Conflicts are avoided by keeping those files open if you're trying to change them.
This has worked quite well but the recent size increase makes problems with people waiting on these files and forgetting to close them a problem.

@@

\subsection{Background}
The identification part of the plan contains useful information about how objects should be treated. One must decide whether or not the object should be under version control. When this should be decided one should ask the question ``Is it necessary to have this object under version control in order to be able to build the complete, working release?''. If the answer to that question is yes, then the object should be configuration item (an item under version control).
Usually, the major part of the object should be under version control. What usually shouldn't be under version control is items such as PM, mails, announcements, memos.
